### 2021-12-09 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@9ef5c83b84870620d756aae345a87dc7b7f08d36 🚀
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@c3703997d21ea0b79a1ffa603d71af7891264633 🚀

\hypertarget{what-are-the-baseline-values-of-thresholding-performance}{%
\subsection{What are the baseline values of thresholding
performance?}\label{what-are-the-baseline-values-of-thresholding-performance}}

ROC-AUC v. PR-AUC, vary \(s\) to simulate a classifier ranging from
no-skill to perfect

>>>>

\begin{figure}
\hypertarget{fig:analytics}{%
\centering
\includegraphics{figures/analytics.png}
\caption{Consequences of changing the classifier skills (\(s\)) and bias
(\(s\)) for a connectance \(\rho=0.15\), on accuracy, \(F_1\), postive
predictive value, and \(\kappa\). \textbf{TODO} discussion of
results}\label{fig:analytics}
}
\end{figure}
